### 2015-05-07 papers/histogram/thesis/thesis.tex
changed to using example results from the more interesting N=25 simulations

Figure \ref{fig:dos_sample} provides an example of an unnormalized
density of states $\tilde D\p{E}$ in energy for a particular
square-well fluid. The density of states has been ``normalized'' to
have a maximum value of $1$ in order to emphasize the logarithmic span
of $D\p{E}$. This logarithmic span ($\sim10^{45}$) is proportional to
the number of moves which one must simulate via Metropolis Monte Carlo
in order to observe the energies with the lowest state densities. For
reference, the world's current fastest supercomputers can perform
$\sim10^{16}$ floating-point operations per second.

\begin{figure}
  \centering
  \includegraphics[width=0.6\textwidth]{figs/dos-sample.pdf}
  \caption[Density of states]{Sample density of states for square-well
    fluid with a well width $\lambda=1.3$, filling fraction
    $\eta=0.3$, and $N=20$ spheres, as computed by several histogram
    methods. The density of states has been normalized to have a
    maximum value of $1$.}
  \label{fig:dos_sample}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.6\textwidth]{figs/transitions-sample.pdf}
  \caption[Transition matrix]{Sample transition matrix $T_d\p{E,\Delta
      E}$ for square-well fluid with a well width $\lambda=1.3$,
    filling fraction $\eta=0.3$, and $N=20$ spheres.  The band at
    $\Delta E=0$ indicates that any given state is most likely to
    transition into another state with the same energy.}
  \label{fig:transitions_sample}
\end{figure}

@@

\begin{figure}[H]
  \centering
  \includegraphics[width=\textwidth]{figs/array-samples.pdf}
  \caption[Sample arrays]{Sample arrays computed by various histogram
    methods for a square-well fluid with a well width $\lambda=1.3$,
    filling fraction $\eta=0.3$, and $N=20$ spheres after simulating
    for $10^5N^2$ iterations: (top left) energy histogram, (top right)
    weight array, (bottom left) density of states.}
  \label{fig:arrays}
\end{figure}

\subsection{Sampling rates}
\label{sec:sampling_rates}

\begin{figure}[H]
  \centering
  \caption[Optimistic energy sampling rates]{Optimistic energy
    sampling rates}
  \label{fig:opt_sample_rate}
\end{figure}

\begin{figure}[H]
  \centering
  \caption[Pessimistic energy sampling rates]{Pessimistic energy
    sampling rates}
  \label{fig:pes_sample_rate}
\end{figure}

>>>>

Figure \ref{fig:dos_sample} provides an example of an unnormalized
density of states $\tilde D\p{E}$ in energy for a particular
square-well fluid. The density of states has been ``normalized'' to
have a maximum value of $1$ in order to emphasize the logarithmic span
of $D\p{E}$. This logarithmic span ($\sim10^{60}$) is proportional to
the number of moves which one must simulate via Metropolis Monte Carlo
in order to observe the energies with the lowest state densities. For
reference, the world's current fastest supercomputers can perform
$\sim10^{16}$ floating-point operations per second.

\begin{figure}
  \centering
  \includegraphics[width=0.6\textwidth]{figs/dos-example.pdf}
  \caption[Density of states]{Sample density of states for square-well
    fluid with a well width $\lambda=1.3$, filling fraction
    $\eta=0.3$, and $N=25$ spheres, as computed by several histogram
    methods. The density of states has been normalized to have a
    maximum value of $1$.}
  \label{fig:dos_sample}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.6\textwidth]{figs/transitions-example.pdf}
  \caption[Transition matrix]{Sample transition matrix $T_d\p{E,\Delta
      E}$ for square-well fluid with a well width $\lambda=1.3$,
    filling fraction $\eta=0.3$, and $N=25$ spheres.  The band at
    $\Delta E=0$ indicates that any given state is most likely to
    transition into another state with the same energy.}
  \label{fig:transitions_sample}
\end{figure}

@@

\begin{figure}[H]
  \centering
  \includegraphics[width=\textwidth]{figs/array-example.pdf}
  \caption[Example arrays]{Example arrays computed by various
    histogram methods for a square-well fluid with a well width
    $\lambda=1.3$, filling fraction $\eta=0.3$, and $N=25$ spheres
    after simulating for $10^5N^2$ iterations: (top left) energy
    histogram, (top right) weight array, (bottom left) density of
    states.}
  \label{fig:arrays}
\end{figure}

\begin{figure}[H]
  \centering
  \includegraphics[width=0.75\textwidth]{figs/sample-rate-example.pdf}
  \caption[Example energy sampling rates]{Example pessimistic energy
    sampling rates computed by various histogram methods for a
    square-well fluid with a well width $\lambda=1.3$, filling
    fraction $\eta=0.3$, and $N=25$ spheres after simulating for
    $10^5N^2$ iterations.}
  \label{fig:sample_rates}
\end{figure}
